Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review

### 2022-01-23 _bookdown_files/04-results.Rmd
Final version

#Load required packages :
library(tidyverse)
library(readr)
library(scales)
library(ggplot2)
library(ggpubr)
library(sunburstR)
library(d3r)

@@

Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focused on a subpopulation of MSM, of those, we identified 7 types of MSM subpopulations : (a) young MSM ; (b) older MSM ; (c) MSM from a racial/ethnic minority ; (d) MSM living with HIV ; (e) MSM engaged in sex work ; (f) Men who have Sex with Men and Women (MSMW) ; and (g) transgender MSM.\
Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r english(sum(population$age == "Older men"))` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r english(sum(population$age == "Adolescent"))` study focuses on adolescents[@Perry].\
Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample.\
`r english(sum(population$race_ethnicity == "Latino"))` studies focus on Latino MSM (LMSM) and `r english(sum(population$race_ethnicity == "Latino & Black"))` study focus on both BMSM and LMSM[@cassels2020].\
Concerning the serologic status of MSM in syndemic literature, `r sum(population$serologic_status == "HIV-positive")` studies are entirely comprised of a sample of MSM living with HIV. Notably, we didn't identify any studies focusing on racial minority MSM living with HIV.\
Finally, the least represented subpopulation of MSM in this review are MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`), MSMW (N = `r sum(population$sex_behav == "MSMW")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).\
Figure \@ref(fig:PlotPop) gives a visual representation of MSM subpopulation's representation in the studies included in this paper.\
In order to obtain the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also took into account studies that did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulations.\
`r .N_disaggregated` studies presented such data : `r .N_dis_BMSMW` for Black MSMW[@dyer2020], `r .N_dis_MSMW` for MSMW[@branstrom; @Mustanski2014; @friedman2014; @ferlatte2018], `r .N_dis_HIVMSM` for MSM living with HIV[@Kurtz2012; @ng2020] and `r .N_dis_LBMSM` for Latino and Black MSM[@Mustanski2017].

>>>>

#Load required packages :
library(tidyverse)
library(readr)
library(scales)
library(ggplot2)
library(ggpubr)
library(sunburstR)
library(d3r)
library(english)

@@

Fewer than half of the studies (N = `r sum(!is.na(population$subpopulation))` ) focused on a subpopulation of MSM, of those, we identified 7 types of MSM subpopulations : (a) young MSM ; (b) older MSM ; (c) MSM from a racial/ethnic minority ; (d) MSM living with HIV ; (e) MSM engaged in sex work ; (f) Men who have Sex with Men and Women (MSMW) ; and (g) transgender MSM.

\
Among studies focusing on a specific age group, `r sum(population$age == "Young adult")` studies focus on young adults, `r english(sum(population$age == "Older men"))` studies focus on older MSM[@zepf2020; @Halkitis2012] and `r english(sum(population$age == "Adolescent"))` study focuses on adolescents[@Perry].

\
Black MSM (BMSM) are the most studied MSM from a racial/ethnic minority (N= `r sum(population$race_ethnicity == "Black")`) but studies focusing on them still represent only `r percent(sum(population$race_ethnicity == "Black")/104)` of our sample.\
`r english(sum(population$race_ethnicity == "Latino"))` studies focus on Latino MSM (LMSM) and `r english(sum(population$race_ethnicity == "Latino & Black"))` study focus on both BMSM and LMSM[@cassels2020].\

Concerning the serologic status of MSM in syndemic literature, `r sum(population$serologic_status == "HIV-positive")` studies are entirely comprised of a sample of MSM living with HIV. Notably, we didn't identify any studies focusing on racial minority MSM living with HIV.

\
Finally, the least represented subpopulation of MSM in this review are MSM engaged in sex work (N = `r sum(population$sex_work == "Sex workers")`), MSMW (N = `r sum(population$sex_behav == "MSMW")`) and transgender MSM (N = `r sum(population$gender_identity == "Transgender")`).

\
Figure \@ref(fig:PlotPop) gives a visual representation of MSM subpopulation's representation in the studies included in this paper.

\
In order to obtain the most comprehensive knowledge of the representation of MSM subpopulations in syndemic literature, we also took into account studies that did not focus on any subpopulation in particular but who presented disaggregated data and analyses for one or more MSM subpopulations.\
`r .N_disaggregated` studies presented such data : `r .N_dis_BMSMW` for Black MSMW[@dyer2020], `r .N_dis_MSMW` for MSMW[@branstrom; @Mustanski2014; @friedman2014; @ferlatte2018], `r .N_dis_HIVMSM` for MSM living with HIV[@Kurtz2012; @ng2020] and `r .N_dis_LBMSM` for Latino and Black MSM[@Mustanski2017].

### 2022-01-23 _bookdown_files/index.Rmd
Final version

---
title: "Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review"
author: 
- "Maxence R. Ouafik^1^, Laetitia Buret^2^, Jean-Luc Belche^3^, Beatrice Scholtes^4^"
- "^1^ Research Unit of Primary Care and Health, General Practice Department University of Liège, Liège, Belgium ; Quartier Hôpital B23 Avenue Hippocrate 13, 4000, Liège <maxence.ouafik@uliege.be> ; Quartier Hôpital B23 Avenue Hippocrate 13 4000 Liège ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
- "^2^ <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
- "^3^  <jlbelche@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-8807-0473"
- "^4^  <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
- "*corresponding author: maxence.ouafik@uliege.be https://orcid.org/0000-0002-9795-5721"

>>>>

---
title: "Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review"
author: 
- "Maxence R. Ouafik^1^, Laetitia Buret^2^, Beatrice Scholtes^3^"
- "^1^ Research Unit of Primary Care and Health, General Practice Department University of Liège, Liège, Belgium ; Quartier Hôpital B23 Avenue Hippocrate 13, 4000, Liège <maxence.ouafik@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
- "^2^ <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
- "^3^  <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
- "*corresponding author: maxence.ouafik@uliege.be https://orcid.org/0000-0002-9795-5721"
